XPath Agent: An Efficient XPath Programming Agent Based on LLM for Web Crawler

### 2024-11-05 paper/main.tex
simple update

The algorithm 1 traverse the HTML tree in a depth-first manner. It removes the invisible or empty nodes and removes all attributes. It's efficient and can be easily implemented in any programming language. In our sampled web pages, the algorithm can reduce the size of the web page by 80\%~90\% on average.

In our implementation, we prompt LLM to extract all information at once on a single page with JSON format. So, multiple fields can be extracted at the same time. Multiple values for a single field might be extracted. We simply treat all extracted values are relevant and passing them to the next stage.

>>>>

The algorithm 1 traverse the HTML tree in a depth-first manner. It removes the invisible or empty nodes, and all attributes. It's efficient and can be easily implemented in any programming language. In our sampled web pages, the algorithm can help us reduce the size of the web page to 10\%~20\% on average.

In our implementation, we prompt LLM to extract all information at once on a single page with JSON format. So, multiple fields can be extracted at the same time. Multiple values for a single field might be extracted. In this case, We simply treat all extracted values are relevant and passing them to the next stage.
